Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-17 2019/emnlp/sparse.tex
title
transformer table

\title{Lexicalized Domain Representation for Neural Machine Translation}

@@

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA & EMEA non-included & EPPS & ECB & Khresmoi & test 2007 (EPPS domain) & newstest 2009 & Newstest 2014 & IWSLT 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 47.6 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 28.56 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 49.43 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.64 & 11.1 \\
 \hline
 EPPS-finetuned & 20.86 & & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 & 28.33 & 11.1 \\
 \hline
 ECB-finetuned & 26.93 & & 27.09 & 56.52 & 22.04 & 22.92 & 12.94 & 17.51 & 13.99 \\
 \hline
 Sparse (1) & 74.26 & 49.9 & 37.67 & 54.07 & 33.85 & 30.86 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse (2) & 73.97 & 49.54 & 37.81 & 53.67 & 34.17 & 30.93 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse (3) &  &  &  & &  &  &  &  & \\
 \hline
 Sparse (4) & 72.95 & 49.78 & 37.62 & 53.35 &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 45.42 & 37.31 & 54.14 & 33.63 & 31.09 &  20.1 & 26.52 & 24.81\\
 \hline
\end{tabularx}
\end{center}

\caption{BPE-detokenized BLEU score for English-French with the Transformer architecture. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse (2) uses generic tag for all of test sets. Sparse (3) uses tag predicted by a pre-trained domain classififer}
\label{tab:1}
\end{table*}

>>>>

\title{Lexicalized Domain Representations for Neural Machine Translation}

@@

\begin{table*}[!h]
\begin{center}
\scalebox{0.81}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & Avg. \\
\hline
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69 $_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$FT_{EMEA}$ & 76.77 $_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$FT_{EPPS}$ & 20.86 $$ & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$FT_{ECB}$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87 $_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26 $_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR_{generic}$ & 73.97 $_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 72.95 $_{49.78}$ & 37.62 & 53.35 & khreshmoi & newstest & iwslt & avg\\
\hline
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$ & 64.57 $_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$FT_{EMEA}$ & 68.35 $$ & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$FT_{EPPS}$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$FT_{ECB}$   & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48 $_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9 $_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg\\
$LDR_{generic}$ & 70.86 $_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 69.51 $_{43.50}$ & 26.31 & 66.86 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture over test sets.}
\end{table*}
